### 2015-11-20 section/5_exper.tex
slight change to figure 3 explanation
change threshold, over limit now

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultful rate} threshold for identifying
0*1? loops, 0.01 as the \textit{resultful rate} threshold for identifying 
[0$|$1]* loops, 0.5 as the \textit{cross-loop redundancy rate}, and 
2 as the \textit{cross-iteration redundancy rate} (i.e., 
the number of distinct iterations is less than half of the total iterations).

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_2$                       & -                       & -                     &   -             & 0$_2$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 12 out of the
14 benign cases. In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
The remaining two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are seven benchmarks in total that each contains
one loop, which generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (i.e., 0*1? resultless). Fortunately,
\Tool run-time analysis counts the total number of loop iterations and
correctly identifies three of them as truly inefficient and severe enough
to cause the corresponding performance problem.
%TODO a table 6 was deleted from oopsla submission

\Tool can also help improve the accuracy of statistical debugging in
identifying which loop is the root cause loop.
For example, the real root-cause loop of Apache\#34464 and GCC\#46401 both
rank number two by the statistical performance diagnosis tool.
Fortunately,
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy.

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses thresholds in its diagnosis.
Intuitively, changing these thresholds affects the
false positive and false negative of \Tool. For example, 
if we change the cross-iteration redundancy rate from the default 2
to 4, \Tool incurs 1 more false negative and 1 fewer false positive.

Our default setting is obtained based on our experience
and should work for many problems.
Developers can adjust these thresholds based on their
need. They can even get rid of all threshods, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative resultless/redundancy nature of suspicious 
loops.

>>>>

As discussed in Section \ref{sec:design}, our analysis contains 
several configurable thresholds. In our evaluation,
we use 0.001 as the \textit{resultful rate} threshold for identifying
0*1? 
%loops, 0.01 as the \textit{resultful rate} threshold for identifying 
and [0$|$1]* resultless loops; we use 
0.5 as the \textit{redundancy rate} threshold for identifying redundant loops.
%, and 
%2 as the \textit{cross-iteration redundancy rate} (i.e., 
%the number of distinct iterations is less than half of the total iterations).

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 11 out of the
13 benign cases. In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
The remaining two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are seven benchmarks in total that each contains
one loop, which generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (i.e., 0*1? resultless). Fortunately,
\Tool run-time analysis counts the total number of loop iterations and
correctly identifies three of them as truly inefficient and severe enough
to cause the corresponding performance problem.

\Tool can also help improve the accuracy of statistical debugging in
identifying which loop is the root-cause loop.
For example, the real root-cause loop of Apache\#34464 and GCC\#46401 both
rank number two by the statistical performance diagnosis tool.
Fortunately,
\Tool can tell that the number one loops in both cases do not contain
any form of inefficiency, resultless or redundancy.

@@

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign report, 
when the rate is 0.75. The trend is similar for resultless
loop checking.

Our default setting %is obtained based on our experience
should work for many problems.
Developers can adjust these thresholds. 
They can even get rid of threshods, and only
use the raw values of resultful/redundancy rates to understand
the absolute and relative (in)efficiency nature of suspicious 
loops. Based on our experiments, the difference between efficient and inefficient
loops is usually obvious, based on these rates.
